### 2014-07-17 ResearchNotes.Rmd
Editing mostly done.  Just doing the  merges on the three data sets.

```{r}

@@

>>>>

```{r}
#Keep only the 5am forecasts
KeyForecasts<-KeyForecasts[as.POSIXlt(KeyForecasts$EvalTime,format="%m/%d/%Y %H:%M:%S")$hour==5,]

#Keep only day ahead
KeyForecasts<-KeyForecasts[(as.POSIXct(KeyForecasts$EvalTime,format="%m/%d/%Y %H:%M:%S") -as.POSIXct(KeyForecasts$Date,format='%m/%d/%Y'))<0,]
summary(KeyForecasts)

@@

Now work on the GoogleSearch terms.  This is only for Pennsylvania.

```{r}
summary(GoogleSearch)

```
Date is actually ISO.  Hope that does not cause a problem.

Merging the three sets.  Just to be clear I need the acutal, forecast from day before and search result from two days before.  That is what I am testing, if I can improve the next day forecast with previous day searches.  Lots of fun date matching ahead.
